### 2023-09-03 sections/2-methods.tex
adding complexity for knn sieves

% Our $k$-NN algorithms do not use two completely distinct phases of coarse and fine search, 
% as is the case in $\rho$-NN search. Still, this distinction is useful in analyzing 
% the asymptotic complexity of $k$-NN search. In particular, we can think of the complexity of 
% coarse search as an estimate of how many clusters we examine during search, and 
% the complexity of fine search as an estimate of how many clusters we must examine all the points 
% from during search, even if we do not actually perform these as two distinct phases.

% To determine the asymptotic complexity of fine search, we must estimate $|F|$, the 
% number of clusters we must examine all the points from during search. With $\rho$-NN 
% search, $F$ is the union of clusters which are within a distance of $r + r_c$ from the query,
% where $r$ is the search radius and $r_c$ is the radius of leaf clusters,
% as in \cite{yu2015entropy}. With $k$-NN search, however, 
% the value of $r$ is dependent on the distance to the $k$th nearest neighbor, which 
% is query-dependent. Thus, for $k$-NN search, we  adjust the definition of 
% $F$ to be the union of clusters which are within a distance of $r' + r_c$ from the query, 
% where $r'$ is the distance to the $k$th nearest neighbor and $r_c$ is defined as before.

% By the triangle inequality, we have that $F \subseteq B(q, r' + 2r_c)$, 
% where $B(q, r' + r_c)$ is the ball of radius $r' + r_c$ centered at $q$.
% Hence, $|F| \leq |B(q, r' + 2r_c)|$.

% Now we have that \begin{align*} \mathbb{E}_q[|B(q, r' + 2r_c)|] &\leq \gamma|B(p, r' + 2r_c)| \\ %because of the assumption that density at different locations on the manifold differ by only a constant factor%
%     &\leq \gamma|B(p, r')|\left(\frac{r' + 2r_c}{r'}\right)^d \label{5}\\ %because d = lfd tells us how the number of additional hits reached scales with a change in radius, and our ratio between radii is (r' + 2r_c)/r'%
%     &\leq \gamma^2 \mathbb{E}[|B(q, r')|]\left(\frac{r'+2r_c}{r'}\right)^d \\ %using density bound again to go from a statement about an arbitrary point back to a statement about the query%
%     &\leq \gamma^2 k\left(\frac{r'+ 2r_c}{r'}\right)^d  \\   %using the fact that for k-nn, the number points in the query ball is k%
% \end{align*}

>>>>

The complexity of the Sieve-based algorithms relies on the assumption that when the cardinalities of clusters is sufficiently close to $k$, the distribution of clusters will mimic the distribution of points in the dataset. 
From this assumption, we can infer that number of clusters which overlap with the query ball is a function of the local fractal dimension near the query point.
In particular, we assume that the number of clusters which overlap the query ball is bounded above by 2$d$, where $d$ is the local fractal dimension of the dataset near the query point, as at each end of each of the $d$ axes, we could have a cluster which overlaps the query ball.

In the worst case scenario, where the data are distributed with uniform density in their embedding space, it takes at most $\log_2{\frac{n}{k}}$ iterations of Sieve to reduce the cardinality of clusters to at most $k$.
